National Longitudinal Evidence for Growth in Subjective Well-being from Spiritual Beliefs

### 2020-12-16 Supplement_And_Analysis.Rmd
typos
checked within/between age estimates using parameters::demean  -- no diff.

---
title             : "Supplement: Analysis for National Longitudinal Evidence for Growth in Subjective Well-being from Spiritual Beliefs"
author: "contact: joseph.bulbulia@gmail.com on behalf of Highland et al."
date: "27/11/2020"
authornote: |
  <!-- https://tinyurl.com/ybremelq -->
# keywords          : "keywords"
wordcount         : no
bibliography      : ["b-references.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
# documentclass     : "apa6"
classoption       : "man"
output            : "html_document"

editor_options: 
  chunk_output_type: console
---

@@

## How many responses waves to select?

@@

mod.1dag2 <-lmer (pwi_formulaDag2, data= d_3)
mod.2dag2 <-lmer (ls_formulaDag2, data= d_3)
```

>>>>

---
title             : "Supplement: Analysis for National Longitudinal Evidence for Growth in Subjective Well-being from Spiritual Beliefs"
author: "contact: joseph.bulbulia@gmail.com on behalf of Highland et al."
date: "27/11/2020"
authornote: |
  <!-- https://tinyurl.com/ybremelq -->
# keywords          : "keywords"
wordcount         : no
bibliography      : ["b-references.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
# documentclass     : "apa6"
classoption       : "man"
output            : "html_document" 
editor_options: 
  chunk_output_type: console
---

@@

## How many waves to select?

@@

mod.1dag2 <-lmer (pwi_formulaDag2, data= d_3)
mod.2dag2 <-lmer (ls_formulaDag2, data= d_3)

dat <- cbind(
  d_3,
  demean(d_3, select = c("Age", "Beliefs"), group = "Id")
)

dat<-dat%>%
  dplyr::mutate(Age_between_C = scale(Age_between, center =TRUE, scale = FALSE))

str(dat)
head(dat$Age_between_C)

# After thought -- check within and between group aging... no differences
# dmPWI <- 'PWI ~  Age_within * Beliefs + Age_between_C  +  Employed + Male + Deprivation_S + Political_Conservativism_S + (1 + Age_within|Id)'
# mod_dmPWI <-lmer (dmPWI, data= dat)
# tab_model(mod_dmPWI)
# summary(mod_dmPWI)
# n1<-ggeffects::ggpredict(model = mod_dmPWI, terms = c("Age_within [minmax]","Beliefs"), 
#                               ci.lvl = 0.95,
#                               type = "fe",
#                               typical = "mean",
#                               back.transform = TRUE,
#                               ppd = FALSE,
#                               interval = "confidence")
#   plot(n1, facets = T) +  gghighlight::gghighlight()  +  theme_blank() #+ ggtitle(y) # title to be suppled
#   
# graph_predictions(mod_dmPWI, "Predicted Values of PWI")
# # 
# lsPWI <- 'LIFESAT ~  Age_within * Beliefs + Age_between_C  +  Employed + Male + Deprivation_S + Political_Conservativism_S + (1 + Age_within|Id)'
# mod_lsPWI <-lmer (lsPWI, data= dat)
# tab_model(mod_lsPWI)
# summary(mod_lsPWI)
# head(dat$Age_within)
# n2<-ggeffects::ggpredict(model = mod_lsPWI, terms = c("Age_within [minmax]","Beliefs"),
#                               ci.lvl = 0.95,
#                               type = "fe",
#                               typical = "mean",
#                               back.transform = TRUE,
#                               ppd = FALSE,
#                               interval = "confidence")
# plot(n2, facets = T) +  gghighlight::gghighlight()  +  theme_blank() #+ ggtitle(y) # title to be suppled

```
